Cybersecurity Is Too Important To Be Left To The Specialists

### 2019-01-27 ITiCSE2019.tex
JHD edits

%%%% Proceedings format for most of ACM conferences (with the exceptions listed below) and all ICPS volumes.
\documentclass[sigconf]{acmart}
\usepackage{paralist}
\usepackage{url}
\usepackage[hyphenbreaks]{breakurl}

@@

Cybersecurity has been in the news for several years, generally prompted by spectacular breaches of one kind or another, such as \cite{BritishAirways2018a}.
It needs attention across the spectrum:
\begin{quote}
change the culture in your organisation around cyber security; to try to do for cyber what has been done so successfully for health and safety, for example, over the last ten years - to get everybody to take it seriously; to take the risk management process seriously and drive that down through the organisation. \cite{Hannigan2019a}\footnote{Former Director of GCHQ: Brittain equivalent of NSA.}
\end{quote}

@@

Specialist curricula abound: a recent one is \cite{ACMIEEEAISSIGSECIFIP}. However, given the shortage of specialists, in practice a good generalist with some CyberSecurity expertise can often get a ``specialist'' job.
\subsection{Research Questions}
\begin{enumerate}
\item The person in the street --- probably not. ({\emph{interesting point from a public engagement/science communication perspective -- aren't ``we'' trying to create a digitally competent and capable citizenry? Minor point but maybe worth mentioning e.g. being safe online, accessing public services, etc}})
\item[JHD]This is important, agreed, but I think this is being a user: think car driving rather than car design. BUT the point I heard from the WC Engineers ``how can security be an option --- safety certainly isn't'' is also relevant.
\item The general CS graduate.
\item The general CS masters graduate.
\item The specialist CS graduate.
\item The specialist CS masters graduate.
\end{enumerate}
%\pagebreak - to fix URL issues
\section{Policy Context}

>>>>

%%%% Proceedings format for most of ACM conferences (with the exceptions listed below) and all ICPS volumes.
%\documentclass[sigconf]{acmart}
\documentclass[sigconf,anonymous]{acmart}
\usepackage{paralist}
\usepackage{url}
\usepackage[hyphenbreaks]{breakurl}

@@

Cybersecurity has been in the news for several years, generally prompted by spectacular breaches of one kind or another, such as \cite{BritishAirways2018a}.
It needs attention across the spectrum:
\begin{quote}
change the culture in your organisation around cyber security; to try to do for cyber what has been done so successfully for health and safety, for example, over the last ten years - to get everybody to take it seriously; to take the risk management process seriously and drive that down through the organisation. \cite{Hannigan2019a}\footnote{Former Director of GCHQ: British equivalent of NSA.}
\end{quote}

@@

Specialist curricula abound: a recent one is \cite{ACMIEEEAISSIGSECIFIP}. However, given the shortage of specialists, in practice a good generalist with some CyberSecurity expertise can often get a ``specialist'' job.
\subsection{Research Questions}
There are various levels of specialism at which CyberSecurity education can be addressed.
\begin{enumerate}
\item The person in the street --- this is important, but there are many initiatives in this area, which are, rightly, largely separated from computing education.
% ({\emph{interesting point from a public engagement/science communication perspective -- aren't ``we'' trying to create a digitally competent and capable citizenry? Minor point but maybe worth mentioning e.g. being safe online, accessing public services, etc}})
%\item[JHD]This is important, agreed, but I think this is being a user: think car driving rather than car design. BUT the point I heard from the WC Engineers ``how can security be an option --- safety certainly isn't'' is also relevant.
\item The general CS graduate.
\item The general CS masters graduate.
\item The specialist CS graduate.
\item The specialist CS masters graduate.
\end{enumerate}
The focus of this paper is on 2--3: the general CS graduate.
%\pagebreak - to fix URL issues
\section{Policy Context}
